Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-12 tex/MesnardoBarba2019.tex
Add snake cost with 3-yr-reserved instances
Cite Freniere et al. (2016)

The top concerns of researchers considering cloud computing are performance and cost. 
Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking. 
Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for Linux virtual machines on the NC-series in 2017.
Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
We present results from benchmarks and test-cases showing that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional university-managed HPC cluster (Colonial One).
Table \ref{tab:hw_specs} lists the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
Our target research application relies on three-dimensional CFD simulations with our in-house research software. We include here a sample of the types of results needed to answer our research question, obtained by running on the public cloud using the reproducible workflow described in Section \ref{sec:workflow}.
The goal is to showcase the potential of cloud computing for CFD, share the lessons we learned in the process, as well as analyze the cost scenarios for full applications.

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

>>>>

The top concerns of researchers considering cloud computing are performance and cost. 
Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization or lack of support for fast networking \cite{freniere_et_2016}.
Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for Linux virtual machines on the NC-series in 2017.
Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
We present results from benchmarks and test-cases showing that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional university-managed HPC cluster (Colonial One).
Table \ref{tab:hw_specs} lists the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
Our target research application relies on three-dimensional CFD simulations with our in-house research software. We include here a sample of the types of results needed to answer our research question, obtained by running on the public cloud using the reproducible workflow described in Section \ref{sec:workflow}.
The goal is to showcase the potential of cloud computing for CFD, share the lessons we learned in the process, as well as analyze the cost scenarios for full applications.

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)
